---
title: "Exponential Simulation"
author: "Matiki"
date: "August 9, 2018"
output: 
  html_document: 
    keep_md: yes
  pdf_document: 
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
We will be investigating the exponential distribution and comparing it to the 
Central Limit Theorem. We will do 1000 simulations of 40 exponentials, and look 
at the distribution of means, as well as the sample variance, and compare them 
to the theoretical mean and variance.

### Exponential Simulation

```{r}
# Set seed
set.seed(42)

# 1000 simulations of 40 exponential random variables
exp_sim <- NULL
num_sims <- 1000
n <- 40
lambda <- 0.2

for (i in 1 : num_sims){
        exp_sim <- c(exp_sim, mean(rexp(n, lambda)))
}
```

### Sample Mean vs Theoretical Mean

```{r}
# Compare sample mean to theoretical (1/lambda = 5)
mean(exp_sim)
```

### Sample Variance vs Theoretical Variance

```{r}
# Compare sample variance to theoretical (1/lambda = 5)
sd(exp_sim) * sqrt(n)
```

### Distribution

```{r}
# Histogram showing distrubution of 1000 random exponential variables
hist(rexp(1000, lambda))

# Histogram showing distribtution of 1000 averages of 40 exponential variables 
hist(exp_sim)
```
