---
title: "Analysis of Tooth Growth Data"
author: "Matiki"
date: "August 9, 2018"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## Overview
We will be analyzing the ToothGrowth data from the R datasets package. The data 
set contains measurements of lengths of cells associated with tooth growth in 60
ginuea pigs. Each animal recieved one of three dose levels of vitamin C, via 
either orange juice or ascorbic acid. We will investigate which dose levels and 
delivery types are associated with tooth growth.

### Exploratory Analysis


### Comparing Tooth Growth by supp and dose

### Conclusion

### Appendix
```{r, eval=FALSE}
# Load necessary R packages
library(dplyr)
library(ggplot2)

# Load data and conduct simple exploratory analysis
data("ToothGrowth")

str(ToothGrowth)
head(ToothGrowth)
summary(ToothGrowth)

# Make plot comparing Tooth length over different supplements and doses 
ggplot(ToothGrowth, aes(x = dose, y = len)) + geom_point(aes(col = supp))

# Check to see if data appear normally distributed
ggplot(ToothGrowth, aes(len)) + geom_histogram()

# Check for equal variance accross supplement types
ToothGrowth %>% group_by(supp) %>%
        summarise(variance = var(len))

# Check for eaual variance accross dose amounts
ToothGrowth %>% group_by(dose) %>%
        summarise(variance = var(len))

# Conduct T test to compare dose amounts (0.5 vs 2.0)
t.test(data = filter(ToothGrowth, dose != 1.0),
       len ~ dose, paired = F, var.equal = F)

# Conduct T test to compare supplement types
t.test(data = ToothGrowth, len ~ supp, paired = F, var.equal = F)

# Conduct T test to compare supp types at dose = 0.5
t.test(data = filter(ToothGrowth, dose == 0.5),
       len ~ supp, paired = F, var.equal = F)
```
